---
title: "Rtextmining"
author: "ChenW"
date: "1/10/2018"
output: html_document
---

## import necessary libraries

```{r}
library('twitteR')
library('httr')
library('tm')
library('ROAuth')
library('SnowballC')
library("wordcloud")
library('RColorBrewer')
```

## assigning twitter credentials

```{r}
key='50PGLiLLdLMpK3u9V5s6BKL4P'
secret='6BbBGc7Ep65sIsCeW1ofJCcPZ36xjGawEe4LercN7u4FUCDYi1'
mytoken='496454062-DBEc6mcugGzQIsODZQOWhkcmbdrGjoGPu4TBka77'
secrettk='hOlSEo5527Dznus0X9lG8oTui4tdcIFvWO7hILkJ55UXF'
```

## set up twitter authorization path

```{r}
setup_twitter_oauth(key,secret,mytoken,secrettk)
```

## search twitter and scrape first 10000 twitts starting from Jan 1st 2018 that mentions 'innovation'

```{r}
test=searchTwitter('innovation', n=10000, since='2018-1-01', lang='en' #, geocode='40.744939,-73.976998,0.5mi'
                   )
```

## apply getText function

```{r}
testlist<-sapply(test,function(x) x$getText())
```

## clean text data and generate a word cloud

```{r}
tcorpus <- Corpus(VectorSource(testlist))
tcorpus <- tm_map(tcorpus, content_transformer(function(x) iconv(x, to='UTF-8-MAC', sub='byte')), mc.cores=1)

inno <- tm_map(tcorpus, content_transformer(tolower))
inno <- tm_map(inno, content_transformer(removePunctuation))
inno <- tm_map(inno,content_transformer(function(x) removeWords(x,stopwords())))
inno <- tm_map(inno,content_transformer(PlainTextDocument))

wordcloud(inno, min.freq=4, scale=c(5,1),
          random.color=F, max.word=45, random.order=F)
```
## get term document matrix

```{r}
testtm<-TermDocumentMatrix(tcorpus)
testtm
```

## get most frequent words

```{r}
findFreqTerms(testtm,lowfreq = 55)
```

## find most associated terms with a specified word

```{r}
findAssocs(testtm,'car',0.4)
```

## create dendrogram

```{r}
tdm<-removeSparseTerms(testtm,sparse=0.93)
tdmscale<-scale(tdm)
dist <- dist(tdmscale, method = "canberra")


par(mai=c(1,1.2,1.0,0.5))
plot(fit,xlab="",sub="",col.main="salmon")
```


